
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Logan Reed} % Your name
\address{(512) 839 - 6662 \\ me@loganreed.org}  % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OVERVIEW}

{I am a graduate student at Rutgers University-Camden, with a focus on Algebra. My current research interests include Finite Group Theory, Vertex Operator Algebra, and Lie Algebras.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Science in Applied Mathematics at Texas State University} \hfill {2018-2021}
\\ 
Minor in Computer Science.
\\
3.78 Upper Level Math GPA.
\\
\\
{\bf Master of Science in Mathematics at Rutgers University-Camden} \hfill {2021-current}


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Relevant Courses}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Honors Graph Theory. \\
%Independent Study in Lie Algebra. \\
%Discrete Mathematics. \\
%Formal Language Theory. \\
%Numerical Analysis. \\ 
%Real and Complex Analysis. \\
%\end{tabular}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work History}

\begin{rSubsection}{Private Math Tutor}{}{2018-current}{}
\item I have tutored over 125 students, with 103 five star reviews. I have helped students in a wide range of subjects. These include K-5 math, collegiate mathematics, and undergraduate computer science. I have extensive experience in both online and in-person environments. If I am accepting new students, you can view my webpage at the following link: https://www.wyzant.com/Tutors/LoganR.

 
\end{rSubsection} 


%------------------------------------------------

\begin{rSubsection}{Math Tutor at Math CATS}{}{2018-2020}{}
\item I tutored through the Department of Mathematics at Texas State. I assisted students in their understanding of the material from undergraduate courses in small study groups. I also gave talks at the beginning of each semester to new students with the goal of student outreach.

\end{rSubsection}

%--------------------------------------------------

\begin{rSubsection}{Math Tutor at the Math and Stats Lab at Rutgers-Camden}{}{2021-2022}{}
\item I tutored through the Department of Mathematics at Rutgers-Camden. I assisted students in their understanding of the material from undergraduate and graduate courses.

\end{rSubsection}

%--------------------------------------------------

\begin{rSubsection}{Part Time Lecturer}{}{Fall 2021}{}
\item I taught an Intro to College Algebra course at Rutgers-Camden. I designed the structure and material of the class independently.

\end{rSubsection}

\begin{rSubsection}{Calculus One TA}{}{Spring 2022}{}
\item I am a Teacher's Assistant for two sections of Calculus One at Rutgers-Camden. I set up the canvas pages, grade homework and exams, and maintain office hours for the students.

\end{rSubsection}

\end{rSection} 

\begin{rSection}{INDEPENDENT STUDY TOPICS}{}{} {}
 \begin{rSubsection}{K-Forcing on the Cartesian product of Simple Graphs}{}{}{}
 \item Finding bounds on the K-Forcing number of the Cartesian product of common families of graphs, such as paths, cycles, and trees.
 \end{rSubsection}
 
 \begin{rSubsection}{Complexes of DiGraph Homomorphisms}{}{}{}
 \item An independent study project to produce results similar to Babson and Kozlov on DiGraphs
 \item I produced a program that can calculate for any DiGraph G, $Hom(K_2,G)$, which will help show which properties of Hom Complexes carry over to DiGraphs.
 \end{rSubsection}
 
  \begin{rSubsection}{A Study on Minimal Prime Graphs of Simple Groups}{}{}{}
  \item An independent study project with the goal of producing new Group Theoretic results using Graph Theory
  \item Focus on an algorithm that can construct every Minimal Prime Graph.
 \end{rSubsection}
 
 \begin{rSubsection}{Lie Algebra}{}{}{}
  \item An independent studies course on the classical results from the algebraic field of Lie Algebra.
 \end{rSubsection}
 
  \begin{rSubsection}{Vertex Operator Algebra}{}{}{}
  \item I am currently working on the field of Vertex Operator Algebra, with the aim of producing a master's thesis from my studies.
 \end{rSubsection}
\end{rSection}

\begin{rSection}{EXTRA CURRICULAR ACTIVITIES}

\begin{rSubsection}{}{} {} {} 
\item A member of the Math Club at Texas State 2018-2020.
\item A member of the Problem Solvers Group at Texas State 2018-2019.
\item Two time Dean's List recipient.
\item Head Martial Arts Instructor from 2016-2018.
\item National and World champion of Kata and Continuous Contact Sparring in 2017 and 2018.
\item Created a program which efficiently takes in a First Order Logic statement and constructs an Analytic Tableaux to determine if the statement is true or false.
\end{rSubsection}

\end{rSection}
%------------------------------------------------


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROGRAMMING SKILLS} \itemsep -3pt  

\item Experience creating procedural visualizations of mathematical concepts
\item 5+ years of Python/C++/C\#/JavaScript
\item 4+ years of \LaTeX

\end{rSection} 


\end{document}
