%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Logan Reed} & Email : \href{mailto:me@loganreed.org}{me@loganreed.org}\\
  & Phone : +1-512-839-6662 \\
  & Github: \href{https://github.com/LoganOReed}{/LoganOReed}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {To Be Decided}{USA}
      {PhD in Applied Mathematics;  GPA: }{Aug. 2024 -- }
    \resumeSubheading
      {Rutgers University}{Camden, NJ}
      {Master of Science in Mathematical Sciences;  GPA: 3.96}{Aug. 2021 -- May. 2023}
    \resumeSubheading
      {Texas State University}{San Marcos, Texas}
      {Bachelor of Science in Applied Mathematics / CS;  GPA: 3.74}{Aug. 2017 -- May. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rutgers University}{Camden, NJ}
      {Researcher in Computational Biology Lab}{Jan 2022 - Current}
      \resumeItemListStart
        \resumeItem{Code Integration}
          {Translated an existing MatLab codebase to a fully documented python package.
            Decoupled data from internal code, implementing the usage of generic API calls and extending the potential uses to any metabolic pathway and database of microarray data.
          }
          \resumeItem{Optimization}{
            Converted the symbolic matrix representation to a numeric model emphasizing vectorization through numpy.
            Improved the flux calculations by writing an ODE function which exclusively uses vectorized matrix operations, decreasing average runtime by $\%5000$
          }
          \resumeItem{Workflows}
          {Created a standardized programming environment using Tox to automate and standardize testing alongside Poetry to manage packages across the entire team. Implemented a CI/CD pipeline using GitLab.}          
          \resumeItem{Data Structures}
          {Wrote a (potentially) novel representation of \textit{metabolic} graphs, synthesizing recent research on representing hypergraphs and ubergraphs.
          }
          \resumeItem{Published Research}
          {Denaro, Christopher et al. “A pipeline for testing drug mechanism of action and combination therapies: From microarray data to simulations via Linear-In-Flux-Expressions: Testing four-drug combinations for tuberculosis treatment.” Mathematical biosciences}

      \resumeItemListEnd

    \resumeSubheading
      {Rutgers University}{Camden, NJ}
      {Part Time Lecturer}{Aug 2021 - Current}
      \resumeItemListStart
        \resumeItem{Instruction}
          {Lectured classes ranging from 30 to 45 students in Introductory College Algebra. Created lesson plans as well as supplementary materials to aid in student comprehension.}
        \resumeItem{Leadership}
          {I was fully in charge of all aspects of the course except the standardized final exam.
          I successfully ran the course, ending with a notably high student satisfaction score.}
      \resumeItemListEnd

    \resumeSubheading
      {Master's Thesis}{Camden, NJ}
      {Graduate Student}{Mar 2022 - May 2023}
      \resumeItemListStart
        \resumeItem{Optimization Algorithm Design}
          {
            Constructed an explicit vector field which allowed the derivative of each vertex to be computed.
            Designed an algorithm which uses a specific form of gradient descent to optimize the location of each vertex while maintaining a constant area.
          }
          \resumeItem{Programming}
          {
            The codebase is a combination of C for IPC, bash for organizing the parallelization, and python as a wrapper and data processing.
          }
          \resumeItem{Results}
          {
            While not notable enough to be published in a journal, there are multiple instances of novel proofs and results.
            Computed constants of interest which had never been published.
          }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeSubItem{Personal Server}
      {Custom built home server that uses Linux and Docker Compose to host various web applications through a reverse proxy.
      Configured a RAID 5 array.
      Automatically updates applications and create backups. }
    \resumeSubItem{Competitive Smash Bros Analysis}
      {
        Scraped and cleaned match data.
        Created visualizations of interesting character and player data.
        Implemented prediction using regression analysis.
      }

    
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C, C++, Python, SQL, Java, LaTeX}
     \hfill
     \textbf{Technologies}{: Excel/LibreOffice, Git, Linux}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
