
I am excited to apply for the Data Science Analyst position at JPMorgan Chase.
During graduate school I gained valuable experience in applying data science methods for large disparate data sets.
As my academic career wraps up, I'm hoping to apply my skills to real world problems like those at JPMorgan Chase.
Banks are the lifeblood of our economy, and I believe working for such a significant bank will amplify the positive impact that I will have.


I began the graduate program with the goal of staying in academia and becoming a research professor.
However, I began working in the Biological Sciences lab applying my mathematics and programming skills toward a real world problem.
This culminated in a paper and accompanying software which calculated the optimal combination of drugs for treating tuberculosis.
While I had no hand in the biological parts of the paper, I found this project vastly superior to my previous research.


My resume is likely unlike other applicants, and I wanted to briefly explain why I would still be a good fit.
During my undergrad, I majored in Applied Math and Minored in CS.
I was only 4 credits away, namely a high level elective, from double majoring.
When factoring in the amount of advanced CS I've done for my thesis, personal projects, and research, I have slightly more experience in this field.
Further, I have a more comprehensive view from rigourous courses on the mathematics behind Machine Learning and Data Science techniques.
Lastly, I would like to address any concerns about possible overqualification.
While I may expect a higher position in a PhD program, I believe that the areas where I am overqualified are balanced by the areas where I lack experience.
Also, even at a PhD program at a top university I would be paid significantly less.


Through my experience as a lecturer and private tutor, I've become very proficient at communicating complex topics to people with diverse backgrounds.
They also gave me immense experience in taking leadership roles and speaking both publicly and one-on-one.
I have worked well in large groups and individually, maintaining deadlines and facilitating open communication.
I am self-motivated with the ability to plan and execute tasks quickly and effectively.
I believe that the combination of my technical skills and my soft skills will make me an invaluable person to have on the team.
