
I am excited to apply for the role of \myPosition{} at Lockheed Martin.
During graduate school I assisted multiple groups of researchers construct pipelines to manage large databases, and I am excited to support \myEmployer{} in a similar way.
I have a huge amount of respect for your ability to use advanced scientific projects to protect the U.S.A, and I'm thrilled to bring my passion and deep understanding to \myEmployer{}.


When I wrote the code for my master's thesis, I faced a few significant technical challenges.
The primary library was in Fortran and was abandoned years ago without documentation.
I created a low-level interface through C to Python and also had to connect it through runner code to GPU parallel computing libraries and a socket-based visualization program.
This code ran on a distributed cloud computing environment owned by Rutgers, and I had to emphasize CI/CD to avoid losing hours of computing power.
The computed data was stored in a MariaDB database, which eventually resulted in my thesis.
I wanted to share this experience since it would be reasonable to see my career thus far as disconnected from the position, but I have a deep knowledge of the field.


The first time I worked under a group of senior-level bosses I was assigned the programming portion of a 15 person research project.
They were biologists and did not have a strong grasp of programming.
Despite this, I exceeded my goals and deadlines, and we rapidly built up a clear line of communication.
Through my experience as a private tutor and lecturer, I've become very proficient at communicating complex topics to people with diverse backgrounds.
I believe that the combination of my technical skills and my soft skills will make me an invaluable person to have on the team.
