
I am excited to apply for the role of \myPosition at \myEmployer.
% (optionally) mention where you saw the opening
% Mention a need of the company and how you can help
% Explain interest in role and company
I totally understand the need you are experiencing, and I have the skills which provide the solution.
As a longtime fan of your products/company/purpose, I'm thrilled to bring my passion and deep understanding to \myEmployer.

% Note keywords in job listing for following
% Give brief overview of relavant background, achievements, skills, specialties
% Give 1 or 2 specific details, and include measurable impacts
Throughout my undergraduate degree I participated in multiple extracurricular activities based on computer graphics and video game platforms.
I have experience in Unity, as well as C++/python interfaces with OpenGL.
More recently, I am currently working on a research project which requires me to visualize solutions to partial differential equations over a polygon.
During this project I use FEM techniques in conjunction with OpenGL to visualize the polygon and solution as it approaches a minimal value.
For this project I also used multiple CI tools, including git, github actions, tox, and poetry, to keep the python environments the same for everyone else on the team.
I am also working on a project through the mathematical biology lab headed by Dr. Piccoli, which should have published results by the end of the year. 

% Give one more specific story or anecdote that displays I'd add value to the company
% Potentially include talk about transferable skills or related experiences from past career
As I get closer to finishing my Masters degree, I am excited to combine my skill in Geometry/Algebra with my skills and passion in computer science.
I have consistently had hobby projects applying my mathematical studies to the realm of computer science, and I would love to further work on the types of projects I am currently researching in an Industry setting.
I believe that the combination of my technical skills and my soft skills will make me an invaluable person to have on the team.
